---
title: "Assignment 2 - The tidyverse"
author: "FILL IN YOUR FULL NAME"
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: no
---
  
<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
```

<!-- Do not forget to input your Github username in the YAML configuration up there --> 

***

```{r, include = T}
# LOAD THE PACKAGES YOU ARE USING IN THIS CODE CHUNK library(nameofpackage)
```

<br>

### Getting started with the Comparative Legislators Database

The Comparative Legislators Database (CLD) includes political, sociodemographic, career, online presence, public attention, and visual information for over 45,000 contemporary and historical politicians from ten countries (see the [corresponding article](https://www.cambridge.org/core/journals/british-journal-of-political-science/article/comparative-legislators-database/D28BB58A8B2C08C8593DB741F42C18B2) for more information). It can be accessed via `legislatoR` - an R package that is available on both [CRAN](https://cran.r-project.org/web/packages/legislatoR/index.html) and [GitHub](https://github.com/saschagobel/legislatoR).

Before you start with the following tasks, skim the tutorial to make yourself familiar with the database. You find it [here](https://cran.r-project.org/web/packages/legislatoR/vignettes/legislatoR.html).

For the following tasks, you will work with ONE of the legislatures. The legislature you'll work with depends on your prename:

| Your prename starts with... | Legislature | Code |
|---------|-------|-------|
| A-C | Austrian Nationalrat | `aut` |
| D-F | Canadian House of Commons | `can` |
| G-I | Czech Poslanecka Snemovna | `cze` |
| J-L | Spanish Congreso de los Diputados | `esp` |
| M-O | French Assemblée | `fra` |
| P-R | German Bundestag | `deu` |
| S-U | Irish Dail | `irl` |
| V-X | UK House of Commons | `gbr` |
| Y-Z | US House of Representatives  | `usa_house` |

The following tasks will be based on data from the `core` and `political` tables of the database.

<br>

***

### Task 1 - Fun with descriptives [X points in total]

a) 

Consider the following numeric vector.

```{r}
library(tidyverse)
library(legislatoR)

dat_core <- get_core(legislature = "deu")
dat_political <- get_political(legislature = "deu")


# entire dataset

# Find out who has got the longest name and who the shortest (both in terms of number of characters)!
# Filter to those with a death date: distribution of age
# Add new variable: age
# Join with political: Distribution of party membership


# only the latest session




```

a)  What's the overall share of female legislators in the entire dataset? [1 point]

```{r}

```

b) How many (both in absolute and relative terms) legislators died in the same place they were born in? [1 point]

```{r}

```

c) Create a new variable `age_at_death` that reports the age at which legislators died. Then, plot the distribution of that variable for the entire dataset. [2 point]

```{r}

```




<br>

***

### Task 2 - Dealing with a character vector  [4 points in total]

Consider the following character vector.

```{r}
friends <- c("Homer", "Marge", "Bart", "Lisa", "Maggie")
```


a) Get the length of the vector. [1 point]

```{r}

```

b) Extract the first two elements of the vector. [1 point]

```{r}

```

c) Extract the second and the last observation from the vector. [1 point]

```{r}

```

d) Sort the elements in reverse alphabetic order. [1 point]

```{r}

```


<br>

***

### Task 3 - A dataset on immigration trips to Ellis Island  [4 points in total]

a) Load the dataset `immigration-ellis.tsv` into R, which contains data on immigration to Ellis Island (1918-1922) by trip. [1 point]

```{r}

```

b) What is the total number of immigration cases in the dataset? [1 point]

```{r}

```

c) From where did the ship with the most immigrants arrive? [1 point]

```{r}

```

d) How many unique ships (according to the name) are in the dataset? [1 point]

```{r}

```

e) Find out the name of the package from the tidyverse that makes working with date and times data easier, and report it below! [1 point]


<!-- During this course, we will input our answers that include text inside the tag, as such:

<div class = "answer"> 
YOU PUT YOUR TEXT HERE
</div> 
 
Also, you will notice that the text you put inside here will not appear in your .html file.
That is because very similar to the # in our R scripts, this is a comment tag for html.
-->

<div class = "answer">

YOUR TEXT SHOULD GO HERE

</div>

