---
title: "Assignment 2 - The tidyverse"
author: "FILL IN YOUR FULL NAME"
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: no
---
  
<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
```


***

```{r, include = T}
# LOAD THE PACKAGES YOU ARE USING IN THIS CODE CHUNK library(nameofpackage)
```

<br>

### Getting started with the Comparative Legislators Database

The Comparative Legislators Database (CLD) includes political, sociodemographic, career, online presence, public attention, and visual information for over 45,000 contemporary and historical politicians from ten countries (see the [corresponding article](https://www.cambridge.org/core/journals/british-journal-of-political-science/article/comparative-legislators-database/D28BB58A8B2C08C8593DB741F42C18B2) for more information). It can be accessed via `legislatoR` - an R package that is available on both [CRAN](https://cran.r-project.org/web/packages/legislatoR/index.html) and [GitHub](https://github.com/saschagobel/legislatoR).

Before you start with the following tasks, skim the tutorial to make yourself familiar with the database. You find it [here](https://cran.r-project.org/web/packages/legislatoR/vignettes/legislatoR.html).

For the following tasks, you will work with ONE of the legislatures. The legislature you'll work with depends on your prename:

| Your prename starts with... | Legislature | Code |
|---------|-------|-------|
| A-C | Austrian Nationalrat | `aut` |
| D-F | Canadian House of Commons | `can` |
| G-I | Czech Poslanecka Snemovna | `cze` |
| J-L | Spanish Congreso de los Diputados | `esp` |
| M-O | French Assemblée | `fra` |
| P-R | German Bundestag | `deu` |
| S-U | Irish Dail | `irl` |
| V-X | UK House of Commons | `gbr` |
| Y-Z | US House of Representatives  | `usa_house` |

The following tasks will be based on data from the `core` and `political` tables of the database.

<br>

***

### Task 1 - Fun with descriptives [8 points in total]

a) What's the overall share of female legislators in the entire dataset? [1 point]

```{r}
# YOUR CODE HERE
```

b) How many (both in absolute and relative terms) legislators died in the same place they were born in? [1 point]

```{r}
# YOUR CODE HERE
```

c) Create a new variable `age_at_death` that reports the age at which legislators died. Then, plot the distribution of that variable for the entire dataset. [2 points]

```{r}
# YOUR CODE HERE
```

d) Provide one single table that provides the 5 legislators with the highest and lowest age at death, ignoring ties. [2 points]

```{r}
# YOUR CODE HERE
```

e) Find out who has got the longest name and who the shortest (both in terms of number of characters, ignoring whitespace)! [2 points]

```{r}
# YOUR CODE HERE
```

<br>

***

### Task 2 - Exploring trends in the data [8 points in total]

a) Using data from all sessions, provide a plot that shows the share of female legislators by session! [3 points]

```{r}
# YOUR CODE HERE
```

b) Explore another relation of variables in the dataset. Your analysis should (i) use data from both the `core` and the `political` table and (ii) feature data from several sessions. Also, offer a brief description and interpretation of your findings! [5 points]

```{r}
# YOUR CODE HERE
```

<div class = "answer">
YOUR ANSWER SHOULD GO HERE
</div>

<br>

***

### Task 3 - Fun with functions [3 points in total]

a) Program a function ultimate_answer() that always returns the number 42, and prove that it works! [1 point]

```{r}
# YOUR CODE HERE
```

b) Program a function normalize() that normalizes a numeric vector x to mean(x) = 0 and sd(x) = 1! Then, apply it to all numeric variables in the mtcars dataset! [2 points]

```{r}
# YOUR CODE HERE
```



